Spatial Analysis

### 2021-11-29 Scripts/spatial_analisis.Rmd
F1 updated with ports

# Get state order from North to south
state_order <- my_path("D","Spatial/grid_eez_sw", name = "grid_eez_sw_df.csv",read = T) %>%
  group_by(state) %>% 
  summarise(
    order = mean(lat)
  ) %>% 
  mutate(abrev = c("CT","DE","ME","MD","MA","NH","NJ","NY","NC","RI","VA")
  ) %>% 
  arrange(desc(order)) %>% 
  mutate(order= c("b","a",letters[3:11])) %>% # weirdly maine goes below
  arrange(order)

# Load grid of state waters
grid_eez_sw_sf <-  st_read(my_path("D","Spatial/grid_eez_sw", name = "grid_eez_sw_sf.shp")) %>%
  select(index,state,geometry) %>% 
  mutate(method = "state_waters",
         state = str_to_sentence(state)) %>% 
  left_join(state_order)

grid_eez_sw_sf$group <- factor(grid_eez_sw_sf$abrev,      # Reordering group factor levels
                               levels = state_order$abrev)

# Load grid of fishing ports
grid_eez_fp_sf <-  st_read(my_path("D","Spatial/grid_eez_fp", name = "grid_eez_fp.shp")) %>%
  select(index,abrev=lndng_s,geometry) %>% 
  mutate(method = "fishing_port"#,
         # state = str_to_sentence(landing_port)
         )%>% 
  left_join(state_order)

grid_eez_fp_sf$group <- factor(grid_eez_fp_sf$abrev,      # Reordering group factor levels
                               levels = state_order$abrev)

@@

p_fp <- gridExtra::grid.arrange(
  # Overall (overlapping) position
  ggplot(data = subset(grid_eez_fp_sf, index != "NA")) +
    geom_sf(data = eez_sf, aes(), fill = "white") + 
    geom_sf(aes(color = group, fill = abrev), alpha = 0.3) +
    geom_sf(data = land_sf, aes()) +
    ggsflabel::geom_sf_label_repel(data = land_sf, aes(label= abrev), 
                                   size = 4,
                                   box.padding = 0.10,
                                   hjust = 1) +
    # scale_color_manual(values = state_pallet) +
    # scale_fill_manual(values = state_pallet) +
    scale_color_manual(values = c(state_pallet[3:4],state_pallet[6:13])) +
    scale_fill_manual(values = c(state_pallet[3:4],state_pallet[6:13])) +
    my_ggtheme_p(leg_pos = "",
                 ax_tx_s = 13) +
    coord_sf(ylim = c(30,48)) +
    scale_y_continuous(breaks = c(30,35,40,45)) +
    labs(x = "", y = "", title = "B) Fishing ports approach") +
    theme(plot.title = element_text(size = 20)),
  # Showing each state separately
  ggplot() +
    geom_sf(data = subset(grid_eez_fp_sf, index = "NA"), color = "white") +
    geom_sf(data = subset(grid_eez_fp_sf, index != "NA"), aes(color = group),size = 0.1, alpha = 0.3) +
    geom_sf(data = land_sf, aes(), fill = "grey80") +
    facet_wrap(~ group) +
    # geom_point(data = rename(ports_df, group = state_postal), aes(x = lon, y = lat), color = "#E6A0C4") +
    theme(legend.position = "top") +
    # scale_color_manual(values = state_pallet,
    scale_color_manual(values = c(state_pallet[3:4],state_pallet[6:13]),
                       # labels = unique(grid_eez_fp_sf$group)) +
                       labels = grid_eez_fp_sf %>% arrange(order) %>%  pull(state) %>% unique()) +
    ggtitle("") +
    my_ggtheme_p(leg_pos = "",
                 ax_tx_s = 11,
                 axx_tx_ang = 45,
                 hjust = 1
    ),
  nrow = 1)

>>>>

# Load grid of state waters
grid_eez_sw_sf <-  st_read(my_path("D","Partial/grid_sw", name = "grid_eez_sw_sf.shp")) %>%
  select(index,state,geometry) %>% 
  mutate(method = "state_waters",
         state = str_to_sentence(state)) %>% 
  left_join(state_lat)

grid_eez_sw_sf$group <- factor(grid_eez_sw_sf$abrev,      # Reordering group factor levels
                               levels = state_lat$abrev)

# Load grid of fishing ports
grid_eez_fp_sf <-  st_read(my_path("D","Partial/grid_fp", name = "grid_eez_fp.shp")) %>%
  select(index,abrev,geometry) %>% 
  mutate(method = "fishing_port"#,
         # state = str_to_sentence(landing_port)
         )%>% 
  left_join(state_lat)

grid_eez_fp_sf$group <- factor(grid_eez_fp_sf$abrev,      # Reordering group factor levels
                               levels = state_lat$abrev)

@@

p_fp <- gridExtra::grid.arrange(
  # Overall (overlapping) position
  ggplot(data = subset(grid_eez_fp_sf, index != "NA")) +
    geom_sf(data = eez_sf, aes(), fill = "white") + 
    geom_sf(aes(color = group, fill = abrev), alpha = 0.3) +
    geom_sf(data = land_sf, aes()) +
    ggsflabel::geom_sf_label_repel(data = land_sf, aes(label= abrev), 
                                   size = 4,
                                   box.padding = 0.10,
                                   hjust = 1) +
    # scale_color_manual(values = state_pallet) +
    # scale_fill_manual(values = state_pallet) +
    scale_color_manual(values = c(state_pallet[3:7],state_pallet[9:11])) +
    scale_fill_manual(values = c(state_pallet[3:7],state_pallet[9:11])) +
    my_ggtheme_p(leg_pos = "",
                 ax_tx_s = 13) +
    coord_sf(ylim = c(30,48)) +
    scale_y_continuous(breaks = c(30,35,40,45)) +
    labs(x = "", y = "", title = "B) Fishing ports approach") +
    theme(plot.title = element_text(size = 20)),
  # Showing each state separately
  ggplot() +
    geom_sf(data = subset(grid_eez_fp_sf, index = "NA"), color = "white") +
    geom_sf(data = subset(grid_eez_fp_sf, index != "NA"), aes(color = group),size = 0.1, alpha = 0.3) +
    geom_sf(data = land_sf, aes(), fill = "grey80") +
    facet_wrap(~ group) +
    # geom_point(data = rename(ports_df, group = state_postal), aes(x = lon, y = lat), color = "#E6A0C4") +
    theme(legend.position = "top") +
    # scale_color_manual(values = state_pallet,
    scale_color_manual(values = c(state_pallet[3:7],state_pallet[9:11]),
                       # labels = unique(grid_eez_fp_sf$group)) +
                       labels = grid_eez_fp_sf %>% arrange(order) %>%  pull(state) %>% unique()) +
    ggtitle("") +
    my_ggtheme_p(leg_pos = "",
                 ax_tx_s = 11,
                 axx_tx_ang = 45,
                 hjust = 1
    ),
  nrow = 1)
